---
title: "Initial Code for Data Manipulation and Modeling"
author: "Nicole Levin"
date: "2022-11-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Start with importing data
```{r}
#Add packages
library(caret)
library(tidyverse)

#Import the data
red_data <- read_delim("winequality-red.csv", delim = ";")
white_data <- read_delim("winequality-white.csv", delim = ";")

#Add variables for type (red or white)
red_data2 <- cbind(red_data, type = "red")
white_data2 <- cbind(white_data, type = "white")

#Conbine datasets
wine_data <- rbind(red_data2, white_data2)
wine_data <- wine_data %>% rename(fixed_acidity = 'fixed acidity', volatile_acidity = 'volatile acidity', citric_acid = 'citric acid', residual_sugar = 'residual sugar', free_SO2 = 'free sulfur dioxide', total_SO2 = 'total sulfur dioxide', qual_orig = 'quality')

#Add variable for quality with >5 = good and otherwise bad
wine_data <- wine_data %>% mutate(quality = if_else(qual_orig >5, "good", "bad") )
wine_data$quality <- factor(wine_data$quality)
wine_data <- wine_data[,-12]
```

Now add in info that will go on the app "pages" starting with the about page.

About this app:
Add details later
```{r}
#Blank code chunk in case I want to add some code related to the about section.
```

Data Exploration:
Here I will add code for doing some numerical and graphical summaries. 
Include a variable for selecting type of plot and type of summary.
Include options to change variables and filter rows.
```{r}
#Input test variable selections
plot_choice <- "scatterplot"
summary_choice <- "mean_sd"
type_choice <- "red"

#Need to think through how we want to do column (variable) selection here
x_var <- "pH"


#Need to add column selection to this
wine_data_subset <- wine_data %>% filter(type_choice)

if(plot_choice = "scatterplot"){
  ggplot(wine_data_subset, aes(x = x_var, y = quality))
}

```

Now setup the modeling page. I need to include logistic regression, a regression tree and a random forest
```{r}
#First split data into training and test set. Set seed for now. Can remove later.
set.seed(371)

#Allow this to be user-defined
prop_choice <- 0.7
m_choice <- 3

train_index <- createDataPartition(wine_data$quality, p=prop_choice, list=FALSE)
data_train <- wine_data[train_index, ]
data_test <- wine_data[-train_index, ]

#Logistic regression fit
regression_fit <-train(quality ~ ., data = data_train, method= "glm", family = "binomial", preProcess = c("center", "scale"), trControl = trainControl(method = "cv", number = 10))

#Tree fit. Need to look at cp tunegrid. May need to be user selected.
tree_fit <-train(quality ~ ., data = data_train, method= "rpart", preProcess = c("center", "scale"), tuneGrid = data.frame(cp = seq(0, 0.1, 0.001)), trControl = trainControl(method = "cv", number = 10))

#Random forest fit.
rf_fit <-train(quality ~ ., data = data_train, method= "rf", preProcess = c("center", "scale"), tuneGrid = data.frame(mtry = m_choice), trControl = trainControl(method = "cv", number = 10))

#Get some results
#Regression
summary(regression_fit$finalModel)
regression_fit$results

#Regression tree
tree_fit$results
plot(tree_fit)

#Random forest. Need to add a plot showing the variable importance?
rf_fit$results


```

Now the prediction tab
```{r}
#Comare using accuracy via confusion matrix
confusionMatrix(regression_fit, newdata = test)
confusionMatrix(tree_fit, newdata = test)
confusionMatrix(rf_fit, newdata = data_test)
```

